---
title: "vectore_like_simulations"
output: html_document
---

#setup
```{r setup, include=FALSE, echo=FALSE,warning = FALSE, message = FALSE}
#warning = FALSE, message = FALSE
#knitr::opts_chunk$set(echo = TRUE)

# clear workspace
rm(list = ls())

library(knitr)

#libraries for data handling:
library(tidyverse)
library(reshape) #for melt/cast
library(Matrix) #A rich hierarchy of matrix classes, including triangular, symmetric, and diagonal matrices, both dense and sparse and with pattern, logical and numeric entries. Numerous methods for and operations on these matrices,
library(standardize) #for the scale_by function

library(geometry) #for the dot function (calculate inner product)
#plotting:
library(ggplot2)
library(ggpubr) #built on ggplot2, I think i use it for the mean_se_ somthing - to show SEM on graphs.
library(gridExtra) #that's for the grid.arrange

#Create a custom color scale
library(RColorBrewer)

#theme for plot:
theme_all_gaps <- theme_classic() +
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1),
        axis.title.x = element_text(size = 26),
        axis.text.x = element_text(size = 14),
        axis.title.y = element_text(size = 26),
        strip.text = element_text(size = 18),
        title = element_text(size = 22),
        legend.text = element_text(size = 18),
        legend.title = element_blank(),
        legend.position = c(0.8, 0.2),
        legend.background = element_rect(fill= rgb(0.9,0.9,0.9)))


```

#DEFINE FUNCTIONS
```{r define functions, include=FALSE, echo=FALSE,warning = FALSE, message = FALSE}
#define norm_vec function
norm_vec <- function(x) sqrt(sum(x^2))

#default values:
max_pat_size=200
act_lim=2
num_steps=10
     
#not in use - I left it here bc maybe the plotting things will be useful
plot_msrs <- function (all_msrs,pat_size,activation) {
  
r_all <- all_msrs[[1]]
spear_all <- all_msrs[[2]]
ndp_all <- all_msrs[[3]] 
ndiff_all <- all_msrs[[4]] 

rownames(r_all) <- pat_size
colnames(r_all) <- activation
rownames(spear_all) <- pat_size
colnames(spear_all) <- activation
rownames(ndp_all) <- pat_size
colnames(ndp_all) <- activation
rownames(ndiff_all) <- pat_size
colnames(ndiff_all) <- activation
r_plot <- melt(r_all) %>% rename_(Pearsons_r = "value")
spear_plot <- melt(spear_all) %>% rename_(Spearman_rho = "value")
ndp_plot <- melt(ndp_all) %>% rename_(ndp = "value")
ndiff_plot <- melt(ndiff_all) %>% rename_(norm_diff = "value")
comb_measures=merge(r_plot,ndp_plot, by= c("X1","X2"))
comb_measures=merge(comb_measures,spear_plot, by= c("X1","X2"))
comb_measures=merge(comb_measures,ndiff_plot, by= c("X1","X2")) %>%
  rename_(num_voxels = "X1",
          activation_level = "X2")

comb_measures <- melt(comb_measures, id=c("num_voxels","activation_level")) %>%
  rename_(measure = "variable")

#plot:
all_spectral<-brewer.pal(9,"Set1")
myspec_all <- all_spectral[c(1,3,4,5)]
myspec2 <- all_spectral[c(1,3,4)]
# labs(title = "half/half activation") +
p_all.1 <- ggplot(comb_measures, aes(x=activation_level,y=value,color=measure)) +
            geom_line() +
            geom_point() +
            scale_color_manual(values = myspec_all) +
            facet_wrap(~num_voxels, nrow=2) +
            theme_classic()

p_all.2 <- ggplot(comb_measures, aes(x=num_voxels,y=value,color=measure)) +
            geom_line() +
            geom_point() +
            scale_color_manual(values = myspec_all) +
            facet_wrap(~activation_level, nrow = 2) +
            theme_classic()

#plot only one graph with Pearson's r and ndp:
sel_msr <- filter(comb_measures,comb_measures$num_voxels==pat_size[5] & !(comb_measures$measure == "norm_diff")) # && comb_measures$measure != "norm_diff"
p_ndp_r <- ggplot(sel_msr, aes(x=activation_level,y=value,color=measure)) +
            geom_line() +
            geom_point() +
            scale_color_manual(values = myspec2) +
            theme_classic()


sel_msr <- filter(comb_measures, comb_measures$measure == "ndp") # 
sel_msr <- sel_msr %>% rename_(overlapping_voxels = "num_voxels")
p_ndp <- ggplot(sel_msr, aes(x=activation_level,y=value,alpha=overlapping_voxels, color = measure)) +
            #geom_line() +
            geom_point() +
            scale_color_manual(values = all_spectral[3]) +
            theme_classic()

p=list(p_all.1,p_all.2,p_ndp_r,p_ndp)
return(p)  

}


###### functions for DG simulation:
calc_msrs_dg <- function (it,pat,rep,all_msrs) {

#within gap1:
save_cors=array(NA,c(4,3))
for (x in c(1,2,3)) {
  pat1=pat[,x];pat2=pat[,(x+1)]
  save_cors[1,x]=cor(pat1,pat2,method = "pearson")
  save_cors[2,x]=cor(pat1,pat2,method = "spearman")
  save_cors[3,x]=dot(pat1,pat2)/(norm_vec(pat1)*norm_vec(pat2)) #ndp
  save_cors[4,x]=abs(norm_vec(pat1)-norm_vec(pat2)) #ndiff_all
}
for (ms in 1:4) {
 all_msrs[[ms]][1,1,rep,it]=mean(save_cors[ms,]) 
}

#within gap2:
save_cors=array(NA,c(4,2))
for (x in c(1,2)) {
  pat1=pat[,x];pat2=pat[,(x+2)]
  save_cors[1,x]=cor(pat1,pat2,method = "pearson")
  save_cors[2,x]=cor(pat1,pat2,method = "spearman")
  save_cors[3,x]=dot(pat1,pat2)/(norm_vec(pat1)*norm_vec(pat2)) #ndp
  save_cors[4,x]=abs(norm_vec(pat1)-norm_vec(pat2)) #ndiff_all
}
for (ms in 1:4) {
 all_msrs[[ms]][1,2,rep,it]=mean(save_cors[ms,]) 
}

#within gap3:
save_cors=array(NA,4)
pat1=pat[,1];pat2=pat[,4]
save_cors[1]=cor(pat1,pat2,method = "pearson")
save_cors[2]=cor(pat1,pat2,method = "spearman")
save_cors[3]=dot(pat1,pat2)/(norm_vec(pat1)*norm_vec(pat2)) #ndp
save_cors[4]=abs(norm_vec(pat1)-norm_vec(pat2)) #ndiff_all
for (ms in 1:4) {
 all_msrs[[ms]][1,3,rep,it]=mean(save_cors[ms]) 
}

#across gap1:
save_cors=array(NA,4)
pat1=pat[,4];pat2=pat[,5]
save_cors[1]=cor(pat1,pat2,method = "pearson")
save_cors[2]=cor(pat1,pat2,method = "spearman")
save_cors[3]=dot(pat1,pat2)/(norm_vec(pat1)*norm_vec(pat2)) #ndp
save_cors[4]=abs(norm_vec(pat1)-norm_vec(pat2)) #ndiff_all
for (ms in 1:4) {
 all_msrs[[ms]][2,1,rep,it]=mean(save_cors[ms]) 
}

#across gap2:
save_cors=array(NA,c(4,2))
for (x in c(3,4)) {
  pat1=pat[,x];pat2=pat[,(x+2)]
  save_cors[1,x-2]=cor(pat1,pat2,method = "pearson")
  save_cors[2,x-2]=cor(pat1,pat2,method = "spearman")
  save_cors[3,x-2]=dot(pat1,pat2)/(norm_vec(pat1)*norm_vec(pat2)) #ndp
  save_cors[4,x-2]=abs(norm_vec(pat1)-norm_vec(pat2)) #ndiff_all
}
for (ms in 1:4) {
 all_msrs[[ms]][2,2,rep,it]=mean(save_cors[ms,]) 
}

#across gap3:
save_cors=array(NA,c(4,3))
for (x in c(2,3,4)) {
  pat1=pat[,x];pat2=pat[,(x+3)]
  save_cors[1,x-1]=cor(pat1,pat2,method = "pearson")
  save_cors[2,x-1]=cor(pat1,pat2,method = "spearman")
  save_cors[3,x-1]=dot(pat1,pat2)/(norm_vec(pat1)*norm_vec(pat2)) #ndp
  save_cors[4,x-1]=abs(norm_vec(pat1)-norm_vec(pat2)) #ndiff_all
}
for (ms in 1:4) {
 all_msrs[[ms]][2,3,rep,it]=mean(save_cors[ms,]) 
}


return(all_msrs)

}     


df_msrs_dg <- function (all_msrs) {

msrs <- c("Pearson","Spearman","ndp","norm_diff")
sum_msrs <- setNames(data.frame(matrix(ncol = 6, nrow = 0)), c("X1","X2","X3","mn","std","measure"))

for (curr_msr in 1:4) {
j=all_msrs[[curr_msr]]
j_mn <- apply(j, c(1,2,3), mean)
j_sd <- apply(j, c(1,2,3), sd)

rownames(j_mn) <- c("within","across")
colnames(j_mn) <- c(1,2,3)
rownames(j_sd) <- c("within","across")
colnames(j_sd) <- c(1,2,3)

j_mn <- melt(j_mn) %>% rename_(mn = "value")
j_sd <- melt(j_sd) %>% rename_(std = "value")
j <- merge(j_mn,j_sd, by= c("X1","X2","X3"))
j$measure <- msrs[curr_msr]

sum_msrs <- rbind(sum_msrs,j)
}

sum_msrs <- sum_msrs %>%
  rename_(event = "X1",
          gap = "X2",
          repetition = "X3")

return(sum_msrs)

}
```
# voxel nums left CA3 and left DG:
>based on (in matlab):
load('/Volumes/data/Bein/Repatime/repatime_scanner/results/encoding/rsa/no_smooth/filtered100s_mtc_clean_mc_wmcsf_3sphere/hipp_voxel_numbers.mat')

>left ca23_025: mean: 39.41, SD: 8.88 range (across subs): 21-60

>left dg_025: mean: 47.8, SD: 9.82 range (across subs): 30-68


# SIMULATION DG MODEL:
### reactivate patterns across reps - don't replace units
This model is currently reported (Jan 2023), for the submission after NN.
```{r SIMULATION DG MODEL reactivate patterns no replacements of units, warning = FALSE, message = FALSE}
#1. Implement the inhibition idea.
#2. Because there's some randomization in how inhibition influences and which voxels will be activated, need to run 500 times and average.
#3. added after NN submission: a problem with the previous model was that it didn't incorporate learning, so we changed this
num_it = 500
act = 1
# init = initiate_patterns_measures(c(0.1,1),act_lim,num_steps)
# overlap = init[[1]]; activation=init[[2]];all_msrs=init[[3]];
#set pt_s:
pt_s = c(40,50,60) #number of voxels - should be divided by 10
pos = 4 #per event
per_act_vox = c(.10,.20) # c(.10,.20,.30,.40,.50) #percentage of activated voxels -make sure pt_s devides well
n_rep=5
initial_inhib=.5 
increase_inhib=(1-initial_inhib)/(n_rep-1) #to have a total of n_rep-1 reach to inhib1
#another option inhibition is a log increase with a base of number of reps - to reach 1 in rep 5.

#inhib = c(0,.25,.5,.75,1) #level of inhibition of the n+1 item - per each repetition
#just linear increase from 0 to 1.

inhib_scale = c(.15,.2,.25) #exponential decay factor - the higher the quicker inhibition decays.
#I thought that exponential makes more sense than linear.
#inhibition is calculated based on: inhib*exp(-inhib_scale*(x-1)), where x is the gap between the items
#for a gap of 1, exp(0)=1, so it's just inhib.

#set up the result mat: within/across by gap (1-3), by num_it
#names are not important - just so I'll remember what's the meaning:
r_all=array(NA, c(2,(pos-1),n_rep,num_it))
spear_all=array(NA, c(2,(pos-1),n_rep,num_it))
ndp_all=array(NA, c(2,(pos-1),n_rep,num_it))
ndiff_all=array(NA, c(2,(pos-1),n_rep,num_it))
all_msrs = list(r_all,spear_all,ndp_all,ndiff_all)

sum_msrs_all <- setNames(data.frame(matrix(ncol = 9, nrow = 0)), c("event","gap","rep","mean","std","measure","per_act_vox","roi_size","inhib_decay_factor"))

 
#loop through pat size and activation levels
for (curr_pts in pt_s) {
  for (curr_actv in per_act_vox) {
    for (curr_in_sc in inhib_scale) {
    print(c(curr_pts,curr_actv,curr_in_sc))
    for (it in 1:num_it) { #per each iteration, run through all reps:
      
      for (rep in 1:n_rep) { #n_rep
        #print(sprintf("##### REP %.0f ######", rep))
          #currently - the only thing that changes across reps is the level of
          #inhibition. The activity pattern for each item is randomly generated each time. Basically, that shouldn't matter for the correlation if it's the same patterns or not in each repetition. If I want to change,I need to think about which neurons are activated again from the prior repetition, and how that works if some of them should be inhibited.
          pat = matrix(0, curr_pts, pos*2) #make place holder for two events
          for (ev in c(1,2)) {
            #for the first position, if first rep, generate a random pattern,
            #if later reps, activate the previous rep pattern (that means that the pattern will be the same for first items across all reps, currently no noise is in the system)
            if (rep == 1) {
              #randomly activate a small part of the pattern (DG, sparse coding):
              rand_loc=sample(1:curr_pts,curr_pts*curr_actv)
              #place in pos1:
              pat[rand_loc,(ev-1)*pos + 1] = act
            } else {
              #print('allocating prev rep')
              pat[,(ev-1)*pos + 1] = prev_pat[,(ev-1)*pos + 1]
            }
              
            #loop through positions:
            for (curr_pos in 2:pos) {
              #check overlap with previous items in the event:
              ch_overlap = 1
              
              #now check, until overlap is satisfied:
              while (ch_overlap == 1) {
                if (rep == 1) {
                  #randomly activate a small part of the pattern (DG, sparse coding):
                  curr_pat=sample(1:curr_pts,curr_pts*curr_actv)
                  #place in pos:
                  #pat[rand_loc,(ev-1)*pos + curr_pos] = act
                } else {
                  #print('allocating prev rep')
                  curr_pat=which(prev_pat[,(ev-1)*pos + curr_pos] == act)
                  #pat[,(ev-1)*pos + curr_pos] = prev_pat[,(ev-1)*pos + curr_pos]
                }
                
                ch_overlap = 0 #assume it's fine
                #now start checking looping through previous items:
                #basically, it could be fine, or not - because inhibition level increased.
                #If not - replace overlap with non-overlapping units.
                #I do that, rather than just removing inhibited units, because that's what our univar and norm-diff data showed:
                #no univar or norm-diff differences across gaps.
                for (back_gap in 1:(curr_pos-1)){
                  # print("curr_pat:")
                  # print(curr_pat)
                  #print(sprintf("back_gap is: %.0f", back_gap))
                  prev = which(pat[,(ev-1)*pos + (curr_pos-back_gap)] == act) #find the ones activated in the previous item
                  #curr_pat = which(pat[,(ev-1)*pos + curr_pos] == act) #either determined by rand_loc, or by previous repetition. Also changed inside this loop.
                  #set inhibition level depending on distance from current item:
                  #logarithmic increase in initial rep - that didn't work so well,
                  #curr_in = log(rep,base=n_rep)*(exp(-curr_in_sc*(back_gap-1))) 
                  #the data shows a linear increase. let's do that:
                  curr_in = (initial_inhib+(rep-1)*increase_inhib)*
                    (exp(-curr_in_sc*(back_gap-1))) #set current level of initial inhibition, based on rep, and gap
                  #print(sprintf("curr_in is: %.2f", curr_in))
                  #how much overlap:
                  replace_pat=ceiling(length(intersect(curr_pat,prev)) - curr_pts*curr_actv*(1-curr_in)) #if the number of activated units allowed is not an integer, needs to ceil so that we'll have enough units replaced.
                  if (replace_pat > 0) { #more than allowed by inhibition levels
                    
                    #of the intersect, sample the ones to take out, at the number that needs to be replaced:
                    #print(intersect(curr_pat,prev))
                    #sample has undesired behavior if the vector it samples from is of length=1, so:
                    if (length(intersect(curr_pat,prev)) == 1) {
                      zero_loc=intersect(curr_pat,prev) #replace the one that is the overlap
                    } else { #if longer, sample
                      zero_loc=sample(intersect(curr_pat,prev),replace_pat)
                    }
                    
                    # print("zero_loc:")
                    # print(zero_loc)
                    #remove them from curr_pat
                    curr_pat=curr_pat[!(curr_pat %in% zero_loc)]
                    
                    if (length(curr_pat) > curr_pts*curr_actv) {
                      print("curr_pat is too long, allocation didn't work")
                      # print("new_loc:")
                      # print(new_loc)
                      # print("zero_loc:")
                      # print(zero_loc)
                      # print("curr_pat:")
                      # print(curr_pat)
                    }
                  } #ends the replace_pat if
                } #ends the for loop for checking back_gap
                #this process can still fault, because it might be we'll replace for overlap btw pos1 and pos3
                #but create overlap btw pos2 and pos3.
                #For now, I don't correct for this explicitly. I check, and if it happened, I sample again.
                
                
                #check if everything is okay:
                for (back_gap in 1:(curr_pos-1)){
                  #print(sprintf("back_gap is: %.0f", back_gap))
                  prev = which(pat[,(ev-1)*pos + (curr_pos-back_gap)] == act) #find the ones activated in the previous item
                  #curr_pat = which(pat[,(ev-1)*pos + curr_pos] == act) #either determined by rand_loc, or by previous repetition
                  #set inhibition level depending on distance from current item:
                  #logaritmic increase didn't work, data is more linear:
                  #curr_in = log(rep,base=n_rep)*(exp(-curr_in_sc*(back_gap-1)))
                  curr_in = (initial_inhib+(rep-1)*increase_inhib)*
                    (exp(-curr_in_sc*(back_gap-1))) #set current level of initial inhibition, based on rep, and gap
                  
                  #print(sprintf("curr_in is: %.2f", curr_in))
                  #how much overlap:
                  replace_pat=length(intersect(curr_pat,prev)) - curr_pts*curr_actv*(1-curr_in) #this is a check - no need to ceil, should be zero or lower.
                  if (replace_pat > 0) { #more than allowed by inhibition levels
                    ch_overlap = 1
                    #print('found overlap, shuffling')
                    break #no need to continue checking more items if one is not good.
                  } #ends the if for checking if overlap is bigger than needed.
                } #ends the loop for checking back_gap
              } #ends the while loop for ch_overlap
              
              #double check all previous items - just to make sure:
              f_w = 0
              for (back_gap in 1:(curr_pos-1)){
                  prev = which(pat[,(ev-1)*pos + (curr_pos-back_gap)] == act)
                  #curr_pat = which(pat[,(ev-1)*pos + curr_pos] == act)
                  #logaritmic increase didn't work, data is more linear:
                  #curr_in = log(rep,base=n_rep)*(exp(-curr_in_sc*(back_gap-1)))
                  curr_in = (initial_inhib+(rep-1)*increase_inhib)*
                    (exp(-curr_in_sc*(back_gap-1))) #set current level of initial inhibition, based on rep, and gap
              
                  if (length(intersect(curr_pat,prev)) > curr_pts*curr_actv*(1-curr_in)) {
                    print("while loop didn't work")
                    f_w = 1
                  }
              } #ends the loop for double checking previous items
                  
              #all previous items are fine - allocate:
              if (f_w == 0) {
                pat[curr_pat,(ev-1)*pos + curr_pos] = act
              } else {
                print('patterns are wrong, fix code')
              }
              
          } #ends the loop of pos 2:pos
        } #ends the loop for event 1/2
          
        #calculate all the measures, per iteration:
        all_msrs = calc_msrs_dg(it,pat,rep,all_msrs)
        #save the pat for the next rep:
        prev_pat <- pat
      } #ends the loop for repetition
    } #ends the loop for number of iterations
    
    #save, and save the params:
    curr_all_msrs <- df_msrs_dg(all_msrs)
    curr_all_msrs$per_act_vox <- curr_actv
    curr_all_msrs$roi_size <- curr_pts
    curr_all_msrs$inhibition <- curr_in_sc
    sum_msrs_all <- rbind(sum_msrs_all,curr_all_msrs)  
    } #ends the loop for inhibition decay level
  } #ends the loop for activation level
} #ends the loop for size of the pattern

sum_msrs_all <- sum_msrs_all %>%
  mutate(upper = mn + std,
         lower = mn - std)

```
### Plot DG simulations
```{r plot DG simulations}
#plot per measure and per activation level:
all_spectral<-brewer.pal(11,"RdYlBu")
myspec_within <-all_spectral[c(2,3,4)]
#myspec_across <-all_spectral[c(10,9,8)] #blues
all_spectral<-brewer.pal(9,"Greys")
myspec_across <-all_spectral[c(4,5,6)] #greys
myspec <-c(myspec_across[2],myspec_within[2])

#choose roi size:
curr_sz = 50
curr_in = .15
curr_msrs_d <- filter(sum_msrs_all,measure == "Pearson" & roi_size == curr_sz & inhibition == curr_in)
p3 <- ggplot(curr_msrs_d, aes(x = gap, y = mn,color = event)) +
  geom_pointrange(data = curr_msrs_d, mapping = aes(x = gap, y = mn, ymin=lower,ymax = upper),position = position_dodge(width = .4),size=1) +
  labs(x = 'Temporal Distance', title = sprintf("Pearson, roi size: %s, rows are percentage activated voxels, cols are repetition",curr_sz)) +
  scale_color_manual(values = myspec) +
  facet_grid(per_act_vox~repetition,scales = "free") + 
  theme_all_gaps +
  theme(legend.position = "none",
        axis.title.y = element_blank()) 

#plot only activation level of .2, different inhibition:
#choose roi size:
curr_sz = 50
curr_actv = .2
curr_msrs_d <- filter(sum_msrs_all,measure == "Pearson" & roi_size == curr_sz & per_act_vox == curr_actv)
p3 <- ggplot(curr_msrs_d, aes(x = gap, y = mn,color = event)) +
  geom_pointrange(data = curr_msrs_d, mapping = aes(x = gap, y = mn, ymin=lower,ymax = upper),position = position_dodge(width = .4),size=1) +
  labs(x = 'Temporal Distance', title = sprintf("Pearson, roi size: %s, rows are inhibition decay, cols are repetition",curr_sz)) +
  scale_color_manual(values = myspec) +
  facet_grid(inhibition~repetition,scales = "free") + 
  theme_all_gaps +
  theme(legend.position = "none",
        axis.title.y = element_blank()) 

#plot only rep5, across inhibition levels and roi sizes:
curr_actv = .2
curr_msrs_d <- filter(sum_msrs_all,measure == "Pearson" & repetition == 5 & per_act_vox == curr_actv)

p_rep5 <- ggplot(curr_msrs_d, aes(x = gap, y = mn,color = event)) +
  geom_pointrange(data = curr_msrs_d, mapping = aes(x = gap, y = mn, ymin=lower,ymax = upper),position = position_dodge(width = .4),size=1) +
  labs(x = 'Temporal Distance', title = sprintf("Pearson, Rep 5, rows are inhibition decay, cols are roi size")) +
  scale_color_manual(values = myspec) +
  facet_grid(inhibition~roi_size,scales = "free") + 
  theme_all_gaps +
  theme(legend.position = "none",
        axis.title.y = element_blank()) 


# p3 <- ggplot(curr_msrs_d, aes(x = gap, y = mn,color = event)) +
#   geom_pointrange(data = curr_msrs_d, mapping = aes(x = gap, y = mn, ymin=lower,ymax = upper),position = position_dodge(width = .4),size=1) +
#   labs(x = 'Temporal Distance') +
#   scale_color_manual(values = myspec) +
#   facet_grid(per_act_vox~inhibition,scales = "free") + 
#   theme_all_gaps +
#   theme(legend.position = "none",
#         axis.title.y = element_blank()) 
# 
# curr_msrs_d <- filter(sum_msrs_all,measure == "ndp" & roi_size == curr_sz)
# p4 <- ggplot(curr_msrs_d, aes(x = gap, y = mn,color = event)) +
#   geom_pointrange(data = curr_msrs_d, mapping = aes(x = gap, y = mn, ymin=lower,ymax = upper),position = position_dodge(width = .4),size=1) +
#   labs(x = 'Temporal Distance', title = sprintf("ndp, roi size: %s, rows are percentage activated voxels, cols are inhibition level",curr_sz)) +
#   scale_color_manual(values = myspec) +
#   facet_grid(per_act_vox~inhibition,scales = "free") + 
#   theme_all_gaps +
#   theme(legend.position = "none",
#         axis.title.y = element_blank())

```
